\racets: Faceted Execution in Racket

### 2018-07-24 paper/paper.tex
removing some obs stuff
spell check for sec2 done

In other applications, Alice might choose a sensible default value to
reveal to others---she may even want to create a \emph{nested}
facet. For example, a social-networking application might use a
nested facet consisting of two labels for
\blue{$\ell_{\text{Friends}}$} and \blue{$\ell_{\text{Family}}$}. A user
could then present three views of her social-media profile: \bmth{p_1} to
her family, containing her phone number and other contact information,
\bmth{p_2} to her friends showing her interests, and \bmth{p_3} to
everyone else, showing only her name and email.

@@

Because the applied function can be stateful, faceted execution also
maintains the current privilege level in a \emph{program counter} (PC). The
program counter is a property of the current evaluation context and is used
to build facets when writes are made to the store in a privileged context.
For example, if a stateful function ``splits'' when applied on both the positive and negative
facets of a value faceted by a label $\blue{\ell}$, and on the positive branch
the function uses $\texttt{set!}$ to mutate a variable $x$ from $2$ to $3$,
FE semantics will set $x$ to $\facet{\ell}{3}{2}$ so that the value $3$
cannot be leaked from the secure context (speculative execution under the
$\blue{+\ell}$ facet). This is because, for the duration of the the app ``split'',
the evaluation context records that all values are implicitly guarded by $\blue{+\ell}$
and then $\blue{-\ell}$, respectively. If the semantics for $\texttt{set!}$ does
not make this faceting explicit, a sensitive value could leak from one PC to another.
We expand upon these subtleties in Section~\ref{sec:semantics},
where we present a complete semantics for faceted execution.

@@

If we had passed any value other than $1$ into the \code{obs} form,
Alice's policy would return \code{false}. In this case, the \code{obs}
form would reduce to $\blue{\star}$, and the program would fail
(indicating that someone other than Alice attempted to view her
board).

@@

Similarly, program counters are sets of branches. However, we must
still ask how we will keep track of the ``current'' program
counter. Our implementation uses Racket's parameters, though other
mechanisms (such as continuation marks\kris{cite}, to which parameters
macro-expand) could also be used. \racets defines the parameter
\code{current-pc}, and updates it as computation progresses:

@@

There is a wealth of existing Racket code we might like to incorporate
into \racets programs. For example, our case study uses the
\texttt{web-server} framework for building web applications. However,
in general, we believe that interacting with code not written using
faceted execution is a challenging open problem, and we do not know of any
principled solutions in the literature.

@@

Several other efforts into dynamic analysis for information flow are
worth noting. \citet{Stefan:2011} first presented \code{LIO}---a monad
(with implementation in Haskell) that tracks privilege of the current
program counter and forbids effects that would violate the security
policy. It might be surprising that \code{LIO}
works well for Haskell programs, given that faceted execution is
more precise than \code{LIO}---allowing values to become faceted
rather than halting the program. One key difference is that Haskell
programs emphasize purity while languages such as
JavaScript (the original target of faceted execution) does not, so much
of the machinery for faceted execution's effect on the store is less
interesting. Several authors have implemented related systems to
\code{LIO}, including variants of faceted execution \cite{Schmitz:2016}
and variants of \code{LIO} that extend its
power to arbitrary monad transformers~\cite{james}. We believe that it
would be possible to implement a variant of our technique that would
give similar insights to programs using \code{LIO}, though much of the
interesting machinery for handling state may be unnecessary.

>>>>

In other applications, Alice may choose a sensible default value to
reveal to others---she may even want to create a \emph{nested}
facet. For example, a social-networking application may use a
nested facet consisting of two labels for
\blue{$\ell_{\text{Friends}}$} and \blue{$\ell_{\text{Family}}$}. A user
can then present three views of her social-media profile: \bmth{p_1} to
her family, containing her phone number and other contact information,
\bmth{p_2} to her friends showing her interests, and \bmth{p_3} to
everyone else, showing only her name and email.

@@

Because the applied function can be stateful, faceted execution also
maintains the current privilege level in a \emph{program counter} (PC). The
program counter is a property of the current evaluation context and is used
to build facets when writes are made to the store in a privileged context.
For example, if a stateful function ``splits'' when applied on both the positive and negative
facets of a value faceted by a label $\blue{\ell}$, and on the positive branch
the function uses $\texttt{set!}$ to mutate a variable $x$ from $2$ to $3$,
FE semantics will set $x$ to $\facet{\ell}{3}{2}$ so that the value $3$
cannot be leaked from the secure context (speculative execution under the
$\blue{+\ell}$ facet). This is because, for the duration of the app ``split'',
the evaluation context records that all values are implicitly guarded by $\blue{+\ell}$
and then $\blue{-\ell}$, respectively. If the semantics for $\texttt{set!}$ does
not make this faceting explicit, a sensitive value can leak from one PC to another.
We expand upon these subtleties in Section~\ref{sec:semantics},
where we present a complete semantics for faceted execution.

@@

@@

Similarly, program counters are sets of branches. However, we must
still ask how we will keep track of the ``current'' program
counter. Our implementation uses Racket's parameters, though other
mechanisms (such as continuation marks\kris{cite}, to which parameters
macro-expand) can also be used. \racets defines the parameter
\code{current-pc}, and updates it as computation progresses:

@@

There is a wealth of existing Racket code we may like to incorporate
into \racets programs. For example, our case study uses the
\texttt{web-server} framework for building web applications. However,
in general, we believe that interacting with code not written using
faceted execution is a challenging open problem, and we do not know of any
principled solutions in the literature.

@@

Several other efforts into dynamic analysis for information flow are
worth noting. \citet{Stefan:2011} first presented \code{LIO}---a monad
(with implementation in Haskell) that tracks privilege of the current
program counter and forbids effects that would violate the security
policy. It may be surprising that \code{LIO}
works well for Haskell programs, given that faceted execution is
more precise than \code{LIO}---allowing values to become faceted
rather than halting the program. One key difference is that Haskell
programs emphasize purity while languages such as
JavaScript (the original target of faceted execution) does not, so much
of the machinery for faceted execution's effect on the store is less
interesting. Several authors have implemented related systems to
\code{LIO}, including variants of faceted execution \cite{Schmitz:2016}
and variants of \code{LIO} that extend its
power to arbitrary monad transformers~\cite{james}. We believe that it
would be possible to implement a variant of our technique that would
give similar insights to programs using \code{LIO}, though much of the
interesting machinery for handling state may be unnecessary.
